---
title: "Reproducing Results of Gerard et al. (2018)"
bibliography: "geno_bib.bib"
output: github_document
---
[![DOI](https://zenodo.org/badge/94825101.svg)](https://zenodo.org/badge/latestdoi/94825101)

# Introduction

This repository contains code to reproduce the empirical evaluations
of @gerard2018genotyping. The new methods can be found in the
[updog](https://cran.r-project.org/package=updog) package on CRAN.

```{r, echo=FALSE, results="hide", message=FALSE, warning=FALSE}
liblist <- list("tidyverse", "updog", "rmutil", "parallel", "parallel", "ggthemes", "gridExtra", "updogAlpha", "fitPoly")
lapply(liblist, require, character.only = TRUE)
```

If you are having trouble reproducing these results, it might be that you need to update some of your R packages. These are the versions that I used:

```{r}
sessionInfo()
```

I've also only tried this out on Ubuntu.

If you find a bug, please create an
[issue](https://github.com/dcgerard/reproduce_genotyping/issues).

# Instructions

To reproduce the results in @gerard2018genotyping, you need to (1) download and install the appropriate packages, (2) obtain the appropriate data, (3) run `make`, and (4) get coffee.

## Install Packages

To install the needed R packages, run the following in R

```{r, eval = FALSE}
install.packages(c("updog", "tidyverse", "rmutil", "snow", "parallel", 
                   "ggthemes", "gridExtra", "devtools", "fitPoly"))
devtools::install_github("dcgerard/updogAlpha")
```

If the most recent CRAN version of `updog` doesn't seem to work, you can retry with the version that I last used to reproduce these results:
```{r, eval = FALSE}
devtools::install_github("dcgerard/updog", 
                         ref = "76c72eb717e18061576fc20b3c07f9da71b67263")
```

Please follow the directions [here](https://github.com/pblischak/polyploid-genotyping/tree/master/ebg) to install `ebg`.

## Get Data

Place [KDRIsweetpotatoXushu18S1LG2017.vcf.gz](https://github.com/dcgerard/KDRIsweetpotatoXushu18S1LG2017) in the Data folder. The direct url is: <https://github.com/dcgerard/KDRIsweetpotatoXushu18S1LG2017/raw/main/KDRIsweetpotatoXushu18S1LG2017.vcf.gz>

## Run Make

To reproduce all of the results in @gerard2018genotyping, simply run
`make` from the terminal. To reproduce the real-data analysis, run
``` bash
make sweet_potato
```
To reproduce the simulations, run
``` bash
make simulations
```

## Get Coffee

The simulations should take a few hours. You should get some coffee. Here is a list of some of my favorite places:

* Washington, D.C.
    - [Politics and Prose](https://www.yelp.com/biz/politics-and-prose-washington)
    - [Colony Club](https://www.yelp.com/biz/colony-club-washington)
* Chicago
    - [Sawada Coffee](https://www.yelp.com/biz/sawada-coffee-chicago)
    - [Plein Air Cafe](https://www.yelp.com/biz/plein-air-cafe-and-eatery-chicago-2)
* Seattle
    - [Bauhaus Ballard](https://www.yelp.com/biz/bauhaus-ballard-seattle)
    - [Cafe Solstice](https://www.yelp.com/biz/cafe-solstice-seattle)
* Columbus
    - [Yeah, Me Too](https://www.yelp.com/biz/yeah-me-too-columbus)
    - [Fox in the Snow](https://www.yelp.com/biz/fox-in-the-snow-cafe-columbus-2)
    - [Stauf's Coffee Roasters](https://www.yelp.com/biz/staufs-coffee-roasters-columbus-2)
    - [Caffe Apropos](https://www.yelp.com/biz/caff%C3%A9-apropos-columbus-2)
    
    
# Note on SuperMASSA

The [source](https://bitbucket.org/orserang/supermassa) is available for SuperMASSA, but it isn't too well documented, so I used the [web application](http://statgen.esalq.usp.br/SuperMASSA/) version during the empirical data analysis. As such, I've committed the inputs and fits in the [Output](https://github.com/dcgerard/reproduce_genotyping/tree/master/Output/supermassa_formatted_data) folder. If you want to generate these fits, you'll have to do it manually.

# References

